### 2024-11-08 Analysis/Spearman.Rmd
Addressed committee meeting comments - 08/11/2024

lr_dat <- data.frame(year = as.factor(acc_surv[2:28,1]), acc_bm = acc_surv[2:28,2], NLFPM_bm = rep$iye, dummy = as.factor(0))

fcar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = lr_dat)

summary(fcar)

plot(ggpredict(fcar, terms = c("NLFPM_bm")))+
  geom_point(data = lr_dat, aes(x = NLFPM_bm, y = acc_bm))

plot(lr_dat$acc_bm~lr_dat$NLFPM_bm)

```
Fall Campelen NLFPM correlation to acoustic - not significant positive relationship (Corr = 0.45, p = 0.0811)

@@

ap_lr_dat <- data.frame(year = as.factor(acc_surv[2:25,1]), acc_bm = acc_surv[2:25,2], NLFPM_bm = ap_rep$iye, dummy = as.factor(0))

@@

scapar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = ap_lr_dat)

summary(scapar)

plot(ggpredict(scapar, terms = c("NLFPM_bm")))+
  geom_point(data = ap_lr_dat, aes(x = NLFPM_bm, y = acc_bm))

plot(ap_lr_dat$acc_bm~ap_lr_dat$NLFPM_bm)

```
Spring Campelen AP NLFPM correlation to acoustic - not significant positive relationship (Corr = 0.54, p = 0.673)

@@

gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:25,1]), acc_bm = acc_surv[2:25,2], NLFPM_bm = gh_rep$iye, dummy = as.factor(0))

# gh_lr_dat <- data.frame(year = c(acc_surv[2:18,1], acc_surv[21:25,1]), acc_bm = c(acc_surv[2:18,2], acc_surv[21:25,2]), 
#                         NLFPM_bm = c(gh_rep$iye[2:18],gh_rep$iye[21:25]))

scghar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = gh_lr_dat)

summary(scghar)

plot(ggpredict(scghar, terms = c("NLFPM_bm")))+
  geom_point(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm))

plot(gh_lr_dat$acc_bm~gh_lr_dat$NLFPM_bm)

```
Spring Campelen GH NLFPM correlation to acoustic - No convergence

@@

# Set up relationship data frame - ACAP
ac_lr_dat <- data.frame(year = as.factor(acc_surv[2:15,1]), acc_bm = acc_surv[2:15,2], NLFPM_bm = ac_rep$iye, dummy = as.factor(0)) #have to y+1

feacar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = ac_lr_dat)

summary(feacar)

plot(ggpredict(feacar, terms = c("NLFPM_bm")))+
  geom_point(data = ac_lr_dat, aes(x = NLFPM_bm, y = acc_bm))

plot(ac_lr_dat$acc_bm~ac_lr_dat$NLFPM_bm)

```
Fall Engel ACAP NLFPM correlation to acoustic - significant positive relationship (Corr = 0.02, p = 0.0376)

@@

gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:15,1]), acc_bm = acc_surv[2:15,2], NLFPM_bm = gh_rep$iye, dummy = as.factor(0))

feghar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = gh_lr_dat)

summary(feghar)

plot(ggpredict(feghar, terms = c("NLFPM_bm")))+
  geom_point(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm))

plot(gh_lr_dat$acc_bm~gh_lr_dat$NLFPM_bm)

```
Fall Engel GH NLFPM correlation to acoustic - No converge

@@

ac_lr_dat <- data.frame(year = as.factor(acc_surv[2:13,1]), acc_bm = acc_surv[2:13,2], NLFPM_bm = c(ac_rep$iye[12], ac_rep$iye[1:11]), dummy = as.factor(0)) #have to y+1

seacar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = ac_lr_dat)

summary(seacar)

plot(ggpredict(seacar, terms = c("NLFPM_bm")))+
  geom_point(data = ac_lr_dat, aes(x = NLFPM_bm, y = acc_bm))

plot(ac_lr_dat$acc_bm~ac_lr_dat$NLFPM_bm)

```
Spring Engel ACAP NLFPM correlation to acoustic - no significant correlation (Corr = 0.03, p = 0.6177)

@@

gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:13,1]), acc_bm = acc_surv[2:13,2], NLFPM_bm = c(gh_rep$iye[12], gh_rep$iye[1:11]), dummy = as.factor(0))

seghar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = gh_lr_dat)

summary(seghar)

plot(ggpredict(seghar, terms = c("NLFPM_bm")))+
  geom_point(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm))

plot(gh_lr_dat$acc_bm~gh_lr_dat$NLFPM_bm)

```
Spring Engel ACAP NLFPM correlation to acoustic - no significant correlation (Corr = 0.09, p = 0.907)

>>>>

lr_dat <- data.frame(year = as.factor(acc_surv[2:28,1]), acc_bm = acc_surv[2:28,2], NLFPM_bm = rep$iye)

cor.test(x = lr_dat$NLFPM_bm, y = lr_dat$acc_bm, method = "spearman")

```
Fall Campelen NLFPM correlation to acoustic - not significant positive relationship (rho = 0.4287, p = 0.05927)

@@

ap_lr_dat <- data.frame(year = as.factor(acc_surv[2:25,1]), acc_bm = acc_surv[2:25,2], NLFPM_bm = ap_rep$iye)

@@

cor.test(x = ap_lr_dat$NLFPM_bm, y = ap_lr_dat$acc_bm, method = "spearman")

```
Spring Campelen AP NLFPM correlation to acoustic - not significant negative relationship (Corr = -0.097, p = 0.684)

@@

gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:25,1]), acc_bm = acc_surv[2:25,2], NLFPM_bm = gh_rep$iye)

cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "spearman")

```
Spring Campelen GH NLFPM correlation to acoustic - not significant negative relationship (Corr = -0.3693, p = 0.109)

@@

# Set up relationship data frame - ACAP
ac_lr_dat <- data.frame(year = as.factor(acc_surv[2:15,1]), acc_bm = acc_surv[2:15,2], NLFPM_bm = ac_rep$iye) #have to y+1

cor.test(x = ac_lr_dat$NLFPM_bm, y = ac_lr_dat$acc_bm, method = "spearman")

```
Fall Engel ACAP NLFPM correlation to acoustic - significant positive relationship (Corr = 0.5272, p = 0.1447)

@@

gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:15,1]), acc_bm = acc_surv[2:15,2], NLFPM_bm = gh_rep$iye)

cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "spearman")

```
Fall Engel GH NLFPM correlation to acoustic - significant positive relationship (rho = 0.6862, p = 0.04124)

@@

ac_lr_dat <- data.frame(year = as.factor(acc_surv[2:13,1]), acc_bm = acc_surv[2:13,2], NLFPM_bm = c(ac_rep$iye[12], ac_rep$iye[1:11])) #have to y+1

cor.test(x = ac_lr_dat$NLFPM_bm, y = ac_lr_dat$acc_bm, method = "spearman")

```
Spring Engel ACAP NLFPM correlation to acoustic - no significant correlation (rho = 0.0838, p = 0.8435)

@@

gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:13,1]), acc_bm = acc_surv[2:13,2], NLFPM_bm = c(gh_rep$iye[12], gh_rep$iye[1:11]))

cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "spearman")

```
Spring Engel ACAP NLFPM correlation to acoustic - no significant correlation (rho = 0.1198, p = 0.7776)
